#Data analyses and figure creation for the Gravitational Frame of Reference Experiment

###Krista E. Strother & Amanda Walker

##Introduction

This file was used to analyze data from my
[Gravitational Frame of Reference Experiment](https://www.youtube.com/watch?v=i9-Vqo_O--o).
All materials including consent, experimental tasks, and debriefing can
be accessed following the previous link and following the links embedded
within the video.  

These data represent observations from 38 participants who reported
participating in existing conditions and emailed me their data. 1
participant reported participating in condition B, but did not indicate
which side the player passed the ball from the visualization task. Therefore,
that participant was excluded.


##Preparing data for analysis

First we need to read in the data.

```{r}
d<-read.csv( "rawdat.csv")
```


Here is a table of the data.

```{r}
mytable<-table(d$Condition,d$Side)
mytable
```
Now we'll use a chi-squared test to determine whether the side of the body (left or right) participants layed on, was independent from their gravitational visualization results.
```{r}
chisq.test(d$Condition,d$Side)
```

This test shows no relationship between condition and side, chi squared(1) = 0, p = 1.

#Summary
There has been conflicting research regarding the gravitational influence on visual perception. The current research is in line with research which shows no relationship between those two variables. 
